%-----------------------------------------------------------------------%
%			       Perfect Curriculum Vitae, Kim Timothy Engh
%-----------------------------------------------------------------------%
\input{kls-cv-13}

\begin{document}
\pagestyle{empty}

	\cvheading{Kim Timothy Engh}
	{kimtengh@gmail.com}{0047}{40070995}
	{Arendalsveien 19D}{4878}{GRIMSTAD}{NORWAY}
	
	\vspace*{10mm}
	
	\cvsection{Key features}
		\cventry{Work experience}{}	{
		 Over 5 years of experience as a service technician / field mechanic at Atlas Copco and in the Norwegian Army. I would for the most part troubleshoot and apply breakdown repairs on surface drilling rigs as well as other types of construction equipment.
		}
		
		\cventry{Positions of trust}{}{
		I served as the union representative for the troop during my time in the Norwegian Army, and until recently I had a position at the board of Mekaunikum, the sorority for mechatronics at UiA.
		}
	
	\cvsection{Education}
		\cventry{Bachelor, Mechatronics}{2011-2014}{
		I am currently studying mechatronics at the University in Agder, UiA. Expected graduation in 2014.
		}
		
		\cventry{Atlas Copco}{2011-2014}{
		I worked as an apprentice at Atlas Copco finishing my education as a construction equipment mechanic. Test passed with highest grade.
		}
		
		\cventry{High School}{2003-2006}{
		A 3 year mechanics education to be a construction equipment mechanic. Studied at Ås VGS and Solør VGS. 
		}
		
	\cvsection{Work Experience}
	
		\cventry{Atlas Copco}{2007-2011}{
		Employed as a service technician working self-reliantly in the field. My tasks mostly consisted of troubleshooting, repairs, and training of customers. My field of expertise lies in surface drilling rigs.
		}
		
		\cventry{Norwegian Army}{2008}
		{I served in the Engineer Battalion as a field mechanic, working in a team doing maintenance and breakdown repairs at camp and in the field. I also served as the union representative for my troop.
		}
		
	\cvsection{Certificates / Training}
		\cventry{General certificates}{}{
		BE, C1E, C, M, T, T1, T2, T4, G4, G8, G20-F, M2, M4 and hot work.
		}
		
		\cventry{Atlas Copco Certified}{}{Certified Atlas Copco service technician. Training consists of courses about electrical systems, hydraulic control systems and specialized Atlas Copco technology.}
		
		\cventry{Basic Engineer}{2008}{
		A course given by the Norwegian Army which consists of hands-on training with the armies construction equipment. The goal was to gain the required knowledge to operate and maintain a large number of machines.
		}
		
		\pagebreak
		
	\cvsection{Other skills}
		\cventry{Languages}{}{
		My native language is Norwegian, but I also have good skills in English.
		}
		
		\cventry{Computer skills}{}{
		I have very good computer skills and I know how to use several different operating systems, such as Linux, Windows and OS X. I also have experience with relevant applications such as $\LaTeX$, Solidworks, Scilab and Maxima.
		}
		
	\cvsection{Personal interests}
		\cventry{Photography}{}{
		My main interest lies in landscape photography. I also enjoy bringing my DSLR along while skiing slalom.
		}
		
		\cventry{Computing}{}{
		Currently i have a few projects based around the open hardware prototyping platform Arduino. This allows me to learn more about using electronic components as well as it's a good way to learn programming. I am writing code in C++ and python.
		}
		
		\cvsection{Attachments}
		\cventry{Grades}{}{
		University in Agder, and certificate of completed apprenticeship.
		}
		
		\cventry{Letter of recommendation}{}{
		Atlas Copco, and the Norwegian Armed Forces.
		}
		
		\cvsection{Note}
		Attachments and references can be delivered upon request in either digital or paper form. I also have a account at LinkedIn. Thanks for taking the time to read my CV.
		
\end{document}
